### 2020-10-21 presentation/5_conclusion.tex
Rev `.gitignore`, rightly commit all images

\Frame {Conclusion}
{
\I We propose a method to estimate MIMO mm-Wave channel \m {\M {H}} by modifying Dantzig Selector (DS), exploiting the sparsity inherent in the problem.

\I We argue for its validity, for the almost-sparse condition in the angular domain, using the effective beamformer \m {\M {P}}, and concerning complex vectors.

\I We propose a bound of the error norm with respect to parameters \m {N_H}, \m {N_Y}, and \m{L}, and investigated the asymptotic behavior of the successful probability.

\I We convert the problem into a linear program to reduce complexity, and run a two-stage version to estimate the position of components.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Future Work}
{
\I Is it possible to reduce complexity, while retaining the performance?

\I Is the trend the same for bigger values of \m {N_H}?

\I Why DS is not as good as expected, and is there any mistakes in the proof of error bound?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {References (1/2)}
{
{\tfx
\I W U Bajwa, J Haupt, A M Sayeed, and R Nowak, \Quote {Compressed channel sensing: A new approach to estimating sparse multipath channels}, \It {Proceedings of the IEEE}, 98(6), 2010

\I S Boyd and L Vandenberghe, \It {Convex optimization}, Cambridge U Press, 2004.

\I E Candès and J Romberg, \Quote {\m {\ell_1}-magic: Recovery of Sparse Signals via Convex Programming}, retrieved online, 2005.

\I E Candès and T Tao, \Quote {The Dantzig Selector: Statistical estimation when \m {p} is much larger than \m {n}}, \It {The Annals of Statistics} 35(6), 2007.
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {References (2/2)}
{
{\tfx
\I E J Candès and T Tao, \Quote {Decoding by Linear Programming}, \It {IEEE Transactions on Information Theory}, 51(12), 2005

\I M P Friedlander and M A Saunders, \Quote {Discussion: the Dantzig selector: statistical estimation when p is much larger than n}, \It {The Annals of Statistics}, 35(6), 2007

>>>>

\Frame {Conclusion}
{
\I We estimate MIMO mm-Wave channel \m {\M {H}} by using a modified DS.

\I We justify DS in present scenario with almost-sparse \m {\V {g}}, and show the RIP of effective beamformer \m {\M {P}}.

\I We propose a error norm analysis of DS in terms of parameters \m {N_H}, \m {N_Y}, and \m{L}, and investigate the asymptotic successful probability.

\I We convert DS into a linear program of lower complexity, and compare another two-stage version of DS.

\I Experiments show DS does appear superior, at the cost of complexity much greater than OMP
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {References (1/2)}
{
{\tfx
\I A Alkhateeb, O E Ayach, G Leus, R W Heath, \Quote {Channel Estimation and Hybrid Precoding for Millimeter Wave Cellular Systems}, \It {IEEE Journal of Selected Topics in Signal Processing} 8(5), 2014

\I A Alkhateeb, G Leus, and R W Heath, \Quote {Compressed sensing based multi-user millimeter wave systems: How many measurements are needed?}, in \It {2015 IEEE International Conference on Acoustics, Speech and Signal Processing}.

\I W U Bajwa, J Haupt, A M Sayeed, and R Nowak, \Quote {Compressed channel sensing: A new approach to estimating sparse multipath channels}, \It {Proceedings of the IEEE}, 98(6), 2010

\I S Boyd and L Vandenberghe, \It {Convex optimization}, Cambridge U Press, 2004.
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {References (2/2)}
{
{\tfx
\I E Candès and J Romberg, \Quote {\m {\ell_1}-magic: Recovery of Sparse Signals via Convex Programming}, retrieved online, 2005.

\I E Candès and T Tao, \Quote {The Dantzig Selector: Statistical estimation when \It {p} is much larger than \It {n}}, \It {The Annals of Statistics} 35(6), 2007.

\I M P Friedlander and M A Saunders, \Quote {Discussion: the Dantzig selector: statistical estimation when \It {p} is much larger than \It {n}}, \It {The Annals of Statistics}, 35(6), 2007.

### 2020-10-21 treatise/1_introduction.tex
Rev `.gitignore`, rightly commit all images

Multiple-input multiple-output (MIMO) communication system will be part of the 5G specification (Rappaport et.\ al.\ \cite [RSM13]).
With a large number of antennae on both transmitter and receiver, MIMO is expected to provide a large signal gain.
The appeal of MIMO includes multiplexing gain (with parallel transmission of data), diversity gain (with redundant transmission using space-time coding), and antenna gain (with beamforming).
The millimeter wave (mm-wave) is also suggested: its smaller wavelength results in higher frequency bands, and thus wider bands available.
The antennae may be closer-spaced, making it possible to increase their number.

However, MIMO also leads to hardware overhead and increases complexity and power consumption.
To design new algorithms that address these issues, it is necessary to obtain channel state information, so that channel capacity, among other metrics, can be calculated.
Not only is the channel estimation difficult due to a large number of antennae, but the transmission is prone to noise corruption.
With more antennae, conventional training-based algorithms also increase in complexity and storage.

@@

Then, a recent developement called compressive sensing turns out to be relevant.
Generally speaking, it is a technique for reconstructing a signal in the case of underdetermined linear systems, if the sparsity of signal guarantees successful recovery in the majority of cases.
A more common situation is that some signals are not sparse in the original basis, but there exists a certain basis on which the signal is sparse, and fewer measurements suffice, though constructing such bases is another undertaking.

@@

The figure shows the signal in both original basis and Hermite polynomials basis.
It is not sparse in the former, but is in the latter.
Thus, the recovery from just a few Hermite polynomial components are able to approximate it well.
(Source: Wikimedia Commons, retrived from \Uurrll {https://commons.wikimedia.org/wiki/File:Orthogonal_Matching_Pursuit.gif})

In the beginning, a Candès and Tao \cite [Can05] pointed out that in various statsitical applications the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, that is,
%
\DispNum {N:p:Nm:Nm} {
\NC N_p \gg \NC N_m \NR
}
%
They showed that in the noiseless case \cite [Can05], it is possible to recover the sparse signal, under a \m {\ell_1}-minimization program, revealing the phenomenon that fewer than \m {N_p} measurement suffices to resonstruct the \m {N_m}-dimensional signal, when it is sparse.

Indeed, usually any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.
But the sparsity constraint essentially restrict the underdetermined system so much that we obtain unique solution for most of the time.

As a practical example, it may be desirable that a camera equipped with few sensors may obtain a lower resolution image, to save computation and storage, and recover the image later, rather than taking a high definition photo at first, and compressing the image later.
Another example is that of medical imaging: surely, since is not only expensive, but also harmful to the body, we may well obtain one image only, while the result can be critically important to assess the patient's well being \cite [CaT07].

@@

But with insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \m {N_p} parameters?
A stronger result was established \cite [CaT07] that, with another \m {\ell_1} minimization program they named The Dantzig Selector (hencefore DS), they can recover the noisy case too, but in doing so, we have to make a few carefully constructed, and seemingly random measurements.

To start, consider \m {\V {x} \in \MB {K} ^{N_p}} and \m {\M {Q} \in \MB {K} ^{N_m \D  N_p}}.
For \m {\MS {A} \subseteq \CB {0, \dots, N_p-1}}, denote
%
\Disp {
\NC \V {x}  _{\SB {\MS {A}}}
=\NC \sum _{i \in \MS {A}} \V {v} \V {u} _{i} \NR
%
\NC \M {Q}  _{\SB {\MS {A}}}
=\NC \sum _{i \in \MS {A}} \M {Q} _{\SB {:,i}} \NR
}
%
That is, respectively, the components of \m {\V {x}}, and the columns of \m {\M {A}}, that have indices in \m {\MS {A}}.

We say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
Formally,
\Result
{Definition}
{
\m {\V {x}} is called \m {s}-sparse, if there is some \m {\MS {A} \subseteq \CB {0, \dots, N_p-1}} such that
%
\DispNum {x:A:x::x:} {
\NC \V {x} _{\SB {\MS {A}}}
=\NC \V {x} \NR
}
%
with
%
\DispNum {A:A:s::s:} {
\NC \Nm {\MS {A}} \leq \NC s. \NR
}
}

@@

Now, consider a linear transformation of real vectors added of noise,
%
\DispNum {y:y:Qx:xz} {
\NC \V {y}
=\NC \M {Q} \V {x} + \V {z} \NR
}
%
where, for example, \m {\V {z}} is an i.i.d.\ normalized Gaussian vector.
How can we hope to estimate \m {\V {x}} when, in addition to insufficient measurements, there is also noise corruption?

@@

They were able to show \cite [CaT07] that Algorithm [3] recovers \m {\V {x}} with the expected square error bounded with overwhelming probability.

From the computational perspective, the formulation as an \m {\ell_1} minimization problem, which is convex, made techniques from convex optimization usable.
Indeed, relevent code has been put on their website for the reader to access and verify (Candès \& Romberg \cite [CaR05]).

Also, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a Linear Program (hereafter LP), rendering convex programming technique applicable.
The constant \m {\d_s} in Definition [2] is crucial, and here we can't just take \m {\M {Q}} to be any unitary matrix, for which it is trivial that \m {\d_s =0}.
One common proposal is choosing every entry of \m {\M {Q}} to be i.i.d., and it can be established that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability (Baraniuk et.\ al.\ \cite [BDD08]).
However it remains a research problem to find RIP matrices efficiently.

Back at the ranch, recall that the overhead of channel estimation has been a concern in the mm-wave MIMO setting.
Luckily, physical evidences suggest that millimeter wave channels are in fact sparse in the frequency domain, and some scholars have thus applied compressive sensing techniques to the problem.
One of the first attempt has been Bajwa et.\ al.\ \cite [BHS10], where they argue that the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
What they explored was the estimation of single-antenna channel response with respect to time.
The accompanying note by the same authors (Bajwa et.\ al.\ \cite [BHR08]) shows that \m {X} is RIP for overwhelming probability, providing the ground for the IEEE paper.
Dealing with a linear time-invariant channel, \cite [BHR08] showed that if the convolution is seen as a linear system, the sensing matrix has RIP of overwhelmingly probability, and DS is ready to be applied, with some nice performance bounds drawing directly from \cite [CaT07].

@@

Still consider \Rf {y:y:Qx:xz}.
We pick up the columns of \m {\M {Q}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}, and thus recovering the original signal.

@@

Alkhateeb et.\ al.\ \cite [AEL14] proposes an adaptive algorithm with a beam codebook for quantized angles of arrival and departure.
Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] discusses the trade-off between number of OMP measurement and accuracy in OMP, applied on an all-phase-shifter beamformers, with quantized, non-uniform, predetermined angles.
Gao et.\ al.\ \cite [LGC16] proposed a jointly reconstruction, with a modified OMP, of several high-dimensional sparse signals with restriction on nonzero-positions.
Hu, Wang, and He \cite [HWH13] applies OMP to estimate quantized path delay of each OFDM subcarrier, assuming the channel gain in each path is stationary.
Lee, Gil, and Lee \cite [LGL16] consider a hybrid system similar to this paper, with the effective beamformer considered as sensing matrix, where they specially designed a set of quantized angles, and in their simulations permuted DFT matrix is used in analog stage.

@@

Ever since, OMP has since been applied in a variety of ways.
Especially, work on channel estimation seems to favored OMP for its low complexity.
One notable drawback of OMP, as pointed out by \cite [GYG18], is that the quantized angle of the sensing matrix used dos not necessarily match the true ones.
Indeed, in the uniform linear array setting, DFT matrix can be used as sensing matrix, but the true angle of arrival and departure is often slightly off.
Meanwhile, as the nature of OMP is greedy, and it is dubious whether it achieves optimality.
In addition, the assumption that the channel matrix is sparse, at least, warrant justification.

>>>>

Multiple-input multiple-output (MIMO) communication system will be part of the 5G specification (Rappaport et.\ al.\ \cite [RSM13]).
With a large number of antennae on both transmitter and receiver, MIMO is expected to provide a large signal gain.
The appeal of MIMO includes multiplexing gain (by parallel transmission of data), diversity gain (by redundant transmission with space-time coding), and antenna gain (by suitable beamforming).
The millimeter wave (mm-wave) is also proposed, since its smaller wavelength, that is higher frequency, results in wider frequency bands available.
The antennae, moreover, may be more closer-spaced, making it possible to increase their number.

However, MIMO also gives rise to higher complexity, hence higher hardware overhead and power consumption.
To design new algorithms that address these issues, it is necessary to obtain channel state information, so that channel capacity, among other metrics, may be found.
Here, not only is the channel estimation difficult, due to the large antennae array, but the transmission in higher frequency is subject to noise corruption too.
Consequently, conventional training-based algorithms now have large time and space complexity.

@@

Indeed, the estimation of MIMO channel amounts to determining all parameters of the channel, which is a big square matrix of dimension same as number of antennae.
Fortunately, physical evidence has suggested that mm-wave channel are poor in scattering \cite [ALS14], reducing the number of paths, and thus the degree of freedom.
And that's when a recent developement called compressive sensing may help.
Generally speaking, it is a technique for reconstructing a underdetermined linear system, if the sparsity of solution guarantees successful recovery in the majority of cases.

@@

It started when Candès and Tao \cite [Can05] noted in various statsitical applications that the number of model parameters \m {N_p \in \MB {N}} is much larger than the number of measurements \m {N_m \in \MB {N}}, that is,
%
\DispNum {N:p:Nm:Nm} {
\NC N_p \gg \NC N_m \NR
}
%
To start, consider \m {\V {x}, \V {x}' \in \MB {K} ^{N_p}} and \m {\M {Q} \in \MB {K} ^{N_m \D  N_p}}, and the linear transformation
%
\DispNum {y:y:Qx:Qx} {
\NC \V {y}
=\NC \M {Q} \V {x} + \V {z} \NR
}
Certainly, \m {\M {Q} \RB {\V {x} - \V {x}'} = 0}, then \m {\V {x}, \V {x}'} are indistinguishable.
But if \m {\V {x}} is sparse, it essentially restrict the system so much that we obtain unique solution for most of the time.

Formally, we say \m {\V {x}} is \m {s}-sparse, if only at most \m {s} components of \m {x} is nonzero.
That is, if there is some \m {\MS {A} \subseteq \CB {0, \dots, N_p-1}} such that
%
\DispNum {x:A:x::x:} {
\NC \V {x} _{\SB {\MS {A}}}
=\NC \V {x} \NR
}
%
with
%
\DispNum {A:A:s::s:} {
\NC \Nm {\MS {A}} \leq \NC s. \NR
}
A more common situation is that some signals are not sparse in the original basis, but there exists a certain basis on which the signal is sparse, though constructing such bases is another undertaking.
(Figure: a signal becomes sparse after transformation of basis.
Retrived from Wikimedia Commons, \Uurrll {https://commons.wikimedia.org/wiki/File:Orthogonal_Matching_Pursuit.gif})

Candès and Tao showed that (\It {ibid}), in the noiseless case, a \m {\ell_1}-minimization program covers the \m {N_m}-dimensional signal, with fewer than \m {N_p} measurement, under overwhelming probability.

As a practical example, it may be desirable that a camera equipped with few sensors may obtain a lower resolution image, to save computation and storage, and recover the image later, rather than taking a high definition photo at first, and compressing the image later.
Such simplification is particularly important in medical imaging, since it is not only expensive, but also harmful to the body, to take too many images, but the imaging accuracy may be critical to the diagnosis (\It {ibid}).

@@

But if the linear transformation is subject to noise,
%
\DispNum {y:y:Qx:xz} {
\NC \V {y}
=\NC \M {Q} \V {x} + \V {z} \NR
}
is it still possible to recover \m {\V {x}}?

We introduce several notions.
For \m {\MS {A} \subseteq \CB {0, \dots, N_p-1}}, denote
%
\Disp {
\NC \V {x}  _{\SB {\MS {A}}}
=\NC \sum _{i \in \MS {A}} \V {v} \V {u} _{i} \NR
%
\NC \M {Q}  _{\SB {\MS {A}}}
=\NC \sum _{i \in \MS {A}} \M {Q} _{\SB {:,i}} \NR
}
%
That is, respectively, the components of \m {\V {x}}, and the columns of \m {\M {A}}, that have indices in \m {\MS {A}}.

@@

For concreteness, say \m {\V {z}} is an i.i.d.\ normalized Gaussian vector.
If so, a stronger result was established \cite [CaT07] that, with another \m {\ell_1} minimization program called Dantzig Selector (hencefore DS), recovery under the noisy case is again possible.

@@

Particularly, Algorithm [2] recovers \m {\V {x}} with the expected square error bounded with overwhelming probability.

From the computational perspective, the formulation as an \m {\ell_1} minimization problem, which is convex, made techniques from convex optimization usable.
Indeed, relevent code has been put on their website for the reader to access and verify (Candès \& Romberg \cite [CaR05]).
Also, the \m {\ell_1}-minimization problem with \m {\ell_\infty}-constraint may be recast as a Linear Program (hereafter LP), rendering convex programming technique applicable.

Here the constant \m {\d_s} in Definition [1] is crucial:
we must make a series of carefully chosen but seemingly random measurement.
We can't just take \m {\M {Q}} to be any unitary matrix, for which it is trivial that \m {\d_s =0}.
One common proposal is choosing every entry of \m {\M {Q}} to be i.i.d., and it can be established that if \m {\VNm {\M {Q} \V {x}}} concentrates sharply, \m {\M {Q}} has RIP for overwhelming probability (Baraniuk et.\ al.\ \cite [BDD08]).
However it remains a research problem to find RIP matrices efficiently.

Back at the ranch, recall that the channel estimation has been considered infeasible in the MIMO setting, but luckily, physical evidences suggest that mm-wave channels are in fact sparse in the frequency domain.
Some scholars have thus applied compressive sensing techniques.
One of the first attempt has been Bajwa et.\ al.\ \cite [BHS10], where they argue that the \m {\ell_0}-norm of the channel matrix may be bounded by a constant, and in such settings the Dantzig Selector may be applied.
What they explored was the estimation of single-antenna channel response with respect to time.
The accompanying note by the same authors (Bajwa et.\ al.\ \cite [BHR08]) shows that \m {X} is RIP for overwhelming probability, providing the ground for the IEEE paper.
Dealing with a linear time-invariant channel, \cite [BHR08] showed that if the convolution is seen as a linear system, the sensing matrix has RIP of overwhelmingly probability, and DS is ready to be applied, with some nice performance bounds drawing directly from \cite [CaT07].

@@

Still consider \Rf {y:y:Qx:xz}.
We pick up the columns of \m {\M {Q}} greedily, hoping to correspond to the nonzero components of \m {\V {x}}.

@@

Ever since, OMP has since been applied in a variety of ways.
Alkhateeb et.\ al.\ \cite [AEL14] proposes an adaptive algorithm with a beam codebook for quantized angles of arrival and departure.
Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] discusses the trade-off between number of OMP measurement and accuracy in OMP, applied on an all-phase-shifter beamformers, with quantized, non-uniform, predetermined angles.
Gao et.\ al.\ \cite [LGC16] proposed a jointly reconstruction, with a modified OMP, of several high-dimensional sparse signals with restriction on nonzero-positions.
Hu, Wang, and He \cite [HWH13] applies OMP to estimate quantized path delay of each OFDM subcarrier, assuming the channel gain in each path is stationary.
Lee, Gil, and Lee \cite [LGL16] consider a hybrid system similar to this paper, with the effective beamformer considered as sensing matrix, where they specially designed a set of quantized angles, and in their simulations permuted DFT matrix is used in analog stage.

@@

From above we note that work on channel estimation seems to favored OMP for its low complexity.
One notable drawback of OMP, as pointed out by \cite [GYG18], is that the quantized angle of the sensing matrix used dos not necessarily match the true ones.
Indeed, in the uniform linear array setting, DFT matrix can be used as sensing matrix, but the true angle of arrival and departure is often slightly off.
Meanwhile, as the nature of OMP is greedy, and it is dubious whether it achieves optimality.
In addition, the assumption that the channel matrix is sparse, at least, warrant justification.
